Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-21 beap_pres_dec2022/beap_pres_dec.tex
Nov 21 Update, Added BEAP presentation slidedeck

% Theme choice: there a number of preset themes to choose from
% Play around with them, Cambridge is nice for first pres
%\usetheme{Szeged}
\usetheme{CambridgeUS} %setting the main theme
\usecolortheme{beaver} % setting colour theme
%\usefonttheme{} %font theme
%\useinnertheme{} %inner theme
%\useoutertheme{} %outer theme

@@

@@

	\section{Introduction}
	% Title page frame
	\begin{frame}
		\titlepage 
	\end{frame}

@@

	% Outline frame
	\begin{frame}{Outline}
		\tableofcontents
	\end{frame}

	% Lists frame
	\section{Lists in Beamer}
	\begin{frame}{Lists in Beamer}

		This is an unordered list:
		\begin{itemize}
			\item Item 1
			\item Item 2
			\item Item 3
		\end{itemize}

		and this is an ordered list:
		\begin{enumerate}
			\item Item 1
			\item Item 2
			\item Item 3
		\end{enumerate}

>>>>

%Defining some colours
\definecolor{darkred}{rgb}{0.8,0,0}

% Theme choice: there a number of preset themes to choose from
% Play around with them, Cambridge is nice for first pres
%\usetheme{Szeged}
\usetheme{CambridgeUS} %setting the main theme
%\usecolortheme{beaver} % setting colour theme
\usefonttheme{professionalfonts} %font theme
%\useinnertheme{} %inner theme
%\useoutertheme{} %outer theme

@@

%Setting colours for boxes
\setbeamercolor{block title}{bg=darkred, fg=white}
\setbeamercolor{block body}{bg=darkred!10}

@@

	% For my introduction slides, there will be the slide with my title and name as well as an outline slide with the brief overview of what I will discuss.
	% Title page frame - SLIDE 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Introduction}
	\begin{frame}
		\titlepage 
	\end{frame}

@@

	% Outline frame - SLIDE 2
	\begin{frame}{Overview}

		\begin{center}
		\begin{minipage}{6cm}

		  		\begin{block}{} Background information \end{block}
		  		\begin{block}{} Research Questions/Explorations \end{block}
		  		\begin{block}{} Experimental Approach \end{block}
		  		\begin{block}{} Results \end{block}

		\end{minipage}
		\end{center}

	% For my Background slides, I will talk about important things such as
	%SLIDE 3 - WHAT ARE LCRs%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Background}
	\begin{frame}{What are LCR's?}

	%SLIDE 4 - I do Not Know if I am including this slide
	\begin{frame}{Information and Entropy Content - MAYBE }

	%SLIDE 5 - LCR's PRESENT IN UNIQUE WAYS
	\begin{frame}{LCR's Present in Unique Ways }

	%SLIDE 6 LCRs are hypermutable
	\begin{frame}{LCR's are Hypermutable }

	%SLIDE 7 - Mechanisms of LCR Evolution
	\begin{frame}{Proposed Mechanisms of LCR Evolution }

	%SLIDE 9 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and Their Evolution? }

	%For my Research questions/Exploration slides, I will talk about things such as
	%SLIDE 10%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Research Questions/Exploration}
	\begin{frame}{What will this Study Explore?}

	%For my Experimental approach slides, I will talk about things such as 
	%SLIDE 11
	\section{Experimental Approach}
	\begin{frame}{What Approach will be Taken?}

	%SLIDE 12
	\begin{frame}{Why use an ABC-MCMC}
